Multimodal Corpora

### 2017-01-16 paper.tex

	\section{First Corpus}
		\Todo{Add first corpus}

@@

				\begin{itemize}
					\item Annotation tier
					\item start point in time
					\item end point in time
					\item annotation value
				\end{itemize}

@@

				\begin{enumerate}
					\item The top tier is the \textbf{sequence}. A sequence contains several gestures directly following each other. There is no so called resting pose between them. No annotation value is assigned on this tier.
					\item The \textbf{phrase} is the tier of a single gesture. This gesture can have one of the following types:
					\begin{description}
						\item[deictic:] A static pointing gesture often involving the index finger. This gesture does not represent something by itself.
						\item[iconic:] A often dynamic gesture describing the object it represents.
						\item[beat:] A rhythmic gesture constisting of two phases. They are used to emphasize or structure the speech.
						\item[discourse:] A gesture used to structure the dialog between the partners.
						\item[move:] This are mostly unconscious movements depicting the emotional state of the subject.
						\item[mixed forms:] It is possible to assign mixed types consisting of the first three types.
					\end{description}
					\item The phrase can be divided in different \textbf{phases}. Following phases can be distinguished:
					\begin{itemize}
						\item Preparation
						\item Stroke
						\item retraction
						\item pre-hold
						\item post-hold
					\end{itemize}
					\item The \textbf{practice} tier describes the meaning of a gesture by the way it is performed. Move, beat and discourse gestures are not annotated this way. Following practices can be assigned:
					\begin{description}
						\item[shaping] an object in the three-dimensional space.
						\item[sizing] an beforehands described object or depicting a distance.
						\item[modelling] an object. The hand itself is the representation of the object.
						\item[drawing] an object in the two-dimensional space.
						\item[pantomiming] an action the pantomime does himself.
						\item[indexing] an direction or to a position.
						\item[grasping] an object.
						\item[counting] with fingers or showing a number of fingers
						\item[hedging] is a methode displaying uncertainty.
					\end{description}					 
					\item The \textbf{perspective} tier describes the viewpoint from which a path is described by a gesture. If items are arranged relative to the speaker the 'speaker' value is assigned, the 'survey' value otherwise.
					\item The \textbf{referent type} tier contains the type of place, object, action, etc. the gesture referes to. Additionally it contains the \textbf{referent name} tier with the name of the reference.
				\end{enumerate}

>>>>

	\section{BAS SmartKom Corpus} 
		The \gls{bas} SmartKom Corpus is a multimodal corpus of audio and video data created during the SmartKom-Project at the University of Munich as a Cooperation between Daimler/Chrysler, DFKI, European Media Lab (EML), Philips, Media Interface, Siemens,	SONY, and the Universities of Erlangen, Munich, Stuttgart. \cite{schiel2002smartkom}. The project finished in 2001 and the resulting corpus was released to the public in July 2002. It consists of annotated and synchronized audio and video files of subjects interacting with the SmartKom User-Interface, with 45 subjects and two 4,5 minute sessions per subject.
		\subsection{Motivation}
			 The goal of the SmartKom-Project  was the development of Computer-User-Interfaces enabling natural interaction.The focus was the investigation of possibilities of multi-modal interaction using natural speech input, two-dimensional gestures and facial expressions.
			 A secondary inquiry was into the possibility of user authentication and verification using the available biometric measures(voice, hand contour and signature).

		\subsection{Recording Scenario}
			The sessions consisted of  Wizard-Of-Oz experiments asking the subjects to solve different tasks without strong guidance. One Task given as an example was the planning of a trip to a cinema, including finding information about nearby cinemas and ordering of tickets. The different Scenarios varied between the sessions and were categorized by
			\begin{itemize}
				\item recording setup (Public, Home or Mobile)
				\item primary task
				\item secondary task
				\item available input methods
				\item recording environment (noise, background of frontal camera)
				\item user profile (gender, age, education, etc.)
			\end{itemize}
		\subsubsection{Experiment Setup}
				The system used for most data acquisition consisted of a graphical tablet onto which the Interface was projected, multiple Microphones as well as four cameras oriented to record facial expressions, a full-body side-view and the interaction area in color and infrared. The output of the system is through the projected graphical interface and synthesized speech and is controlled as an Wizard of Oz Experiment with two wizards in a separate Room controlling the experiment.

		\Todo{Add first corpus}

@@

				\begin{itemize}
					\item Annotation tier
					\item Start point in time
					\item End point in time
					\item Annotation value
				\end{itemize}

@@

				\begin{enumerate}
					\item The top tier is the \textbf{sequence}. A sequence contains several gestures directly following each other. There is no so called resting pose between them. No annotation value is assigned on this tier.
					\item The \textbf{phrase} is the tier of a single gesture. This gesture can have one of the following types:
					\begin{description}
						\item[deictic:] A static pointing gesture often involving the index finger. This gesture does not represent something by itself.
						\item[iconic:] A often dynamic gesture describing the object it represents.
						\item[beat:] A rhythmic gesture constisting of two phases. They are used to emphasize or structure the speech.
						\item[discourse:] A gesture used to structure the dialog between the partners.
						\item[move:] This are mostly unconscious movements depicting the emotional state of the subject.
						\item[mixed forms:] It is possible to assign mixed types consisting of the first three types.
					\end{description}
					\item The phrase can be divided in different \textbf{phases}. Following phases can be distinguished:
					\begin{itemize}
						\item Preparation
						\item Stroke
						\item Retraction
						\item Pre-hold
						\item Post-hold
					\end{itemize}
					\item The \textbf{practice} tier describes the meaning of a gesture by the way it is performed. Move, beat and discourse gestures are not annotated this way. Following practices can be assigned:
					\begin{description}
						\item[shaping] an object in the three-dimensional space.
						\item[sizing] an beforehands described object or depicting a distance.
						\item[modelling] an object. The hand itself is the representation of the object.
						\item[drawing] an object in the two-dimensional space.
						\item[pantomiming] an action the pantomime does himself.
						\item[indexing] an direction or to a position.
						\item[grasping] an object.
						\item[counting] with fingers or showing a number of fingers
						\item[hedging] is a methode displaying uncertainty.
					\end{description}					 
					\item The \textbf{perspective} tier describes the viewpoint from which a path is described by a gesture. If items are arranged relative to the speaker the 'speaker' value is assigned, the 'survey' value otherwise.
					\item The \textbf{referent type} tier contains the type of place, object, action, etc. the gesture referes to. Additionally it contains the \textbf{referent name} tier with the name of the reference.
				\end{enumerate}
